{ \fontfamily{ptm}\selectfont Catalyst Meta Acceleration Framework: The Gist of its Theories }

### 2024-11-07 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

\title{
    {
        \fontfamily{ptm}\selectfont 
        A Title Here: A Sub Title Here
    }
    }

\author{
    Hongda Li
    \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
    The University of British Columbia, Kelowna, BC Canada V1V 1V7. E-mail:  \texttt{alto@mail.ubc.ca}.}~ and~Xianfu Wang
    \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
    The University of British Columbia, Kelowna, BC Canada V1V 1V7. E-mail:  \texttt{shawn.wang@ubc.ca}.}
}

@@

\begin{abstract} 
    \noindent
    Abstract example citation \cite{bezanson_julia_2017}.

@@

\section{Introduction}

    \subsection{Contributions}

\section{Preliminaries}\label{sec:preliminaries}

>>>>

\title{
    {
        \fontfamily{ptm}\selectfont 
        Catalyst Meta Acceleration Framework: The Gist of its Theories
    }
    }

\author{
    Hongda Li
    \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
    The University of British Columbia, Kelowna, BC Canada V1V 1V7. E-mail:  \texttt{alto@mail.ubc.ca}.}~ and~Xianfu Wang
    % \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
    % The University of British Columbia, Kelowna, BC Canada V1V 1V7. E-mail:  \texttt{shawn.wang@ubc.ca}.}
}

@@

\begin{abstract} 
    \noindent
    Nesterov's accelerated gradient first appeared back in the 1983 has sparked numerous theoretical and pratical advancedments in Mathematics programming literatures. 
    The idea behind Nesterov's acceleration is universal in the convex case and it has concrete extension in the non-convex case. 
    In this paper we survey specifically the Catalyst Acceleration that incorperated ideas from the Accelerated Proximal Point Method proposed by Guller back in 1993. 
    We will review Nesterov's classical analysis of accelerated gradient in the convex case. 
    We summarize key aspect of the theoretical innovations involved to achieve the design of the algorithm in convex, and non-convex case. 
    \cite{bezanson_julia_2017}.

@@

\section{Introduction}
    \subsection{Literature reviews}    
    \subsection{Contributions}

\section{Preliminaries}\label{sec:preliminaries}
    \subsection{Method of Nesterov's Estimating Sequence}

\section{Nesterov's Accelerated Proximal Gradient}
\section{Guller 1993}
\section{H.Lin 2015}

\section{Nonconvex Extension of Catalyst Acceleration}
